---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CruzPlot

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/smwoodman/CruzPlot.svg?branch=master)](https://travis-ci.com/smwoodman/CruzPlot)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/smwoodman/CruzPlot?branch=master&svg=true)](https://ci.appveyor.com/project/smwoodman/CruzPlot)
<!-- badges: end -->

CruzPlot is an R package that contains a GUI for creating maps, plotting data, and performing basic data summaries from data files in the "DAS" format produced by WinCruz.

## Installation

You can install CruzPlot from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools") # Install devtools package if needed
devtools::install_github("smwoodman/swfscDAS")
devtools::install_github("smwoodman/CruzPlot")
```

If your version of CruzPlot is outdated, running the above command will install the new version. However, if you want to reinstall the same version of CruzPlot, you can run:

```{r, eval=FALSE}
devtools::install_github("smwoodman/CruzPlot", force = TRUE)
```

Before installing CruzPlot, you must have [R](https://www.r-project.org/), [RStudio](https://rstudio.com/products/rstudio/download/#download), and the appropriate version of [Rtools](https://cran.r-project.org/bin/windows/Rtools/) installed. It is best practice to install after closing all instances of R and RStudio, and then running the install code from the R GUI rather than RStudio. Please contact the developer if you have any issues.

After updating, it is recommended to create and save new workspaces, rather than using workspaces saved with a previous version of CruzPlot.

## Run CruzPlot

To open and run CruzPlot, run the following code in RStudio:

```{r, eval=FALSE}
CruzPlot::cruzplot_gui()
```

## CruzPlot manual

The CruzPlot manual can be downloaded [at this link](https://github.com/smwoodman/CruzPlot/blob/master/inst/shiny/www/CruzPlot_Manual_app.pdf), or accessed when running CruzPlot by opening the "CruzPlot Manual" page. It is recommended for new users to read the first two pages of the manual for orientation purposes; the rest of the manual contains section-specific information (formatting requirements, etc.) and can be read on an as-needed basis.

## Additional details

If text or images overlap within the CruzPlot window, you can make the browser window full screen or adjust the text size in your browser (e.g., Ctrl - minus ('-') on Windows systems)
