---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CruzPlot

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/smwoodman/CruzPlot.svg?branch=master)](https://travis-ci.com/smwoodman/CruzPlot)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/smwoodman/CruzPlot?branch=master&svg=true)](https://ci.appveyor.com/project/smwoodman/CruzPlot)
<!-- badges: end -->

`CruzPlot` is an R package that contains a GUI for creating maps, plotting data, and performing basic data summaries from data files in the "DAS" format produced by WinCruz.

## Installation

You can install `CruzPlot` from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("remotes") # Install remotes package if needed
remotes::install_github("smwoodman/swfscDAS")
remotes::install_github("smwoodman/CruzPlot")
```

Note that CruzPlot depends on swfscDAS, and thus you should ensure that [swfscDAS](https://smwoodman.github.io/swfscDAS/) is installed and updated as well. Running the above code will ensure the latest versions of both packages are installed. However, if you want to force an installation, you can run:

```{r, eval=FALSE}
remotes::install_github("smwoodman/swfscDAS", force = TRUE)
remotes::install_github("smwoodman/CruzPlot", force = TRUE)
```

Before installing `CruzPlot`, you must have [R](https://www.r-project.org/), [RStudio](https://rstudio.com/products/rstudio/download/#download), and the appropriate version of [Rtools](https://cran.r-project.org/bin/windows/Rtools/) installed. It is best practice to install after closing all instances of R and RStudio, and then running the install code from the R GUI rather than RStudio. Please contact the developer if you have any issues.

After updating, it is recommended to create and save new workspaces, rather than using workspaces saved with a previous version of `CruzPlot.`

## Running CruzPlot

To open and run `CruzPlot`, run the following code in RStudio:

```{r, eval=FALSE}
CruzPlot::cruzplot_gui()
```

If text or images overlap within the `CruzPlot` window, you can make the browser window full screen or adjust the text size in your browser (e.g., Ctrl - minus ('-') on Windows systems)

## CruzPlot manual

The `CruzPlot` manual can be downloaded [at this link](https://github.com/smwoodman/CruzPlot/blob/master/inst/shiny/www/CruzPlot_Manual_app.pdf), or accessed when running `CruzPlot` by opening the "CruzPlot Manual" page. It is recommended for new users to read the first two pages of the manual for orientation purposes; the rest of the manual contains section-specific information (formatting requirements, etc.) and can be read on an as-needed basis.
